---
title: "Exploring_motif_validation_scores"
author: "Ashton Omdahl"
date: "March 6, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(tidyr)
library(magrittr)
```
We are looking at  the summary of our scores, trying to decide where thre threshold needs to be. I think 0.8 is probably good, will give us to TFs

```{r}
setwd("D:/AshtonData/MPI_all_data/SummaryFiles_8-17/")
tf_reference_match_scores <- read_tsv("./All_comparisons_summary.txt") %>% separate(Split, c("pTF_mod", "refTF"), "_against_") %>% separate(pTF_mod, c("pTF_family", "pTF_i"), "-N")  %>% mutate(pTF = paste0("N", pTF_i))
print(tf_reference_match_scores)
```
Let's take a look at the distribution of the scores, how many are above our cutoff of 0.8

```{r pressure, echo=FALSE}
hist(tf_reference_match_scores$Score)
sum(tf_reference_match_scores$Score > 0.8)
```

Let's take a look at those ones above 80- how many have unique identifiers and sequences and come from unique sources?
```{r}
top_match_scores <- tf_reference_match_scores %>% filter(Score >= 0.8) %>% select(-Dir_name, -Rank, -pTF_i) %>% distinct()%T>% print()

write_tsv(tf_reference_match_scores %>% select(-Dir_name, -Rank, pTF_i) %>% distinct(),"D:/AshtonData/MPI_all_data/SummaryFiles_8-17/unique_pTFs_all_3_6.tsv")


#%>% mutate(ID = paste0(pTF,"_", refTF, "_", Comparison_seq, "_", Reference_seq, "_", Source)) %>% distinct() 
```

Wow, that's still 170! Let's see how many unique pTFs we've identified
```{r}
length(unique(top_match_scores$pTF))
unique(top_match_scores$pTF)
```
Point of interest: what is the distribution of categories on these highly filtered pTFs?
```{r}
library(ggplot2)
ggplot(top_match_scores, aes(x = Source)) + geom_histogram(stat = 'count', fill = "seagreen")

```
So this graph tells us something about the internal consistency of datasets. Basically these bars show us how many pTFs were validated  by a given method. Self-identified TFs are far more frequent.
```{r}
TFIntersections <- function(type1, type2)
{
  print(paste("TFs found by both", type1, "and", type2))
  total_num <- unique(length(filter(top_match_scores, Source == type1)$pTF))
  intersect_num <-sum(unique(filter(top_match_scores, Source == type1)$pTF) %in% unique(filter(top_match_scores, Source == type2)$pTF))
  print(paste("This represents", intersect_num/total_num, "of", type1, "total pTFs"))
  unique(filter(top_match_scores, Source == type1)$pTF[filter(top_match_scores, Source == type1)$pTF %in% filter(top_match_scores, Source == type2)$pTF])
}

TFIntersections("RNA-RNA", "MA-MA")
TFIntersections("RNA-RNA", "MA-RNA")
TFIntersections("RNA-RNA", "RNA-MA")
print("")
TFIntersections("MA-MA", "RNA-RNA")
TFIntersections("MA-MA", "MA-RNA")
TFIntersections("MA-MA", "RNA-MA")
print("")
TFIntersections("MA-RNA", "RNA-RNA")
TFIntersections("MA-RNA", "MA-MA")
TFIntersections("MA-RNA", "RNA-MA")
print("")
TFIntersections("RNA-MA", "RNA-RNA")
TFIntersections("RNA-MA", "MA-RNA")
TFIntersections("RNA-MA", "MA-MA")

```

This leads to the next question: are there any TFs that fall into all four categories? Into other subsets of them?
```{r}
TFOverlaps <- function(type1, type2)
{
unique(filter(top_match_scores, Source == type1)$pTF[filter(top_match_scores, Source == type1)$pTF %in% filter(top_match_scores, Source == type2)$pTF])
  }

TFOverlaps("RNA-RNA", "MA-MA") -> rrmm
TFOverlaps("RNA-RNA", "MA-RNA") -> rrmr
TFOverlaps("RNA-RNA", "RNA-MA") -> rrrm
TFOverlaps("RNA-RNA", "RNA-RNA") -> rrrr
rr_list <- c(rrmm, rrmr, rrrm)
ggplot(data.frame(rr_list), aes(x=rr_list)) + geom_histogram(stat = "count", fill = "seagreen") + scale_y_continuous(breaks = seq(0,5,by=1)) + xlab(label = "TFs identified") + ggtitle("RNA-RNA TF Cross-validation Frequency")



TFOverlaps("MA-MA", "RNA-RNA") -> mmrr
TFOverlaps("MA-MA", "MA-RNA") ->mmmr
TFOverlaps("MA-MA", "RNA-MA") -> mmrm
TFOverlaps("MA-MA", "MA-MA") -> mmmm
mm_list <- c(mmrr,mmmr,mmrm)
ggplot(data.frame(mm_list), aes(x=mm_list)) + geom_histogram(stat = "count", fill = "coral") + scale_y_continuous(breaks = seq(0,5,by=1)) + xlab(label = "TFs identified") + ggtitle("MA-MA TF Cross-validation Frequency")




TFOverlaps("MA-RNA", "RNA-RNA") -> mrrr
TFOverlaps("MA-RNA", "MA-MA") -> mrmm
TFOverlaps("MA-RNA", "RNA-MA") -> mrrm
TFOverlaps("MA-RNA", "MA-RNA") -> mrmr
mr_list <- c(mrrr,mrmm,mrrm)
ggplot(data.frame(mr_list), aes(x=mr_list)) + geom_histogram(stat = "count", fill = "dodgerblue2") + scale_y_continuous(breaks = seq(0,5,by=1)) + xlab(label = "TFs identified") + ggtitle("MA-RNA TF Cross-validation Frequency")


TFOverlaps("RNA-MA", "RNA-MA") -> rmrm
TFOverlaps("RNA-MA", "RNA-RNA") -> rmrr
TFOverlaps("RNA-MA", "MA-RNA") -> rmmr
TFOverlaps("RNA-MA", "MA-MA")-> rmmm
rm_list <- c(rmrr, rmmr, rmmm)
ggplot(data.frame(rm_list), aes(x=rm_list)) + geom_histogram(stat = "count", fill = "gold") + scale_y_continuous(breaks = seq(0,5,by=1)) + xlab(label = "TFs identified") + ggtitle("RNA-MA TF Cross-validation Frequency")


```
Viewing the plots on top of each other:
```{r fig.height = 7, fig.width=10}
library(reshape)
to_plot <- top_match_scores %>% select(pTF, Source) 
tf_unique_list <- to_plot$pTF
ggplot(to_plot, aes(x=pTF, fill = Source))+ geom_bar(stat = "count", position = "identity", alpha  = 0.3) + scale_y_continuous(breaks = seq(0,12, by  =2)) +  coord_flip()

```
We can show this more concisely with a venn diagram
```{r}
mm_all <- (top_match_scores %>% filter(Source == "MA-MA") %>% select(pTF) %>% unique())$pTF
rr_all <- (top_match_scores %>% filter(Source == "RNA-RNA") %>% select(pTF) %>% unique())$pTF
rm_all <- (top_match_scores %>% filter(Source == "RNA-MA") %>% select(pTF) %>% unique())$pTF
mr_all <- (top_match_scores %>% filter(Source == "MA-RNA") %>% select(pTF) %>% unique())$pTF

library(gplots)
venn(list("MA-MA"=mm_all, "RNA-RNA"=rr_all, "MA-RNA" = mr_all, "RNA-MA" = rm_all))
```
This tells us that the datasets are fairly indpendent of each other, all only cover 1

So now we have lists with everything in them; I am curious to know which motifs appear the most frequently across these lists. That will give us a sense for the ones most conserved (?)
```{r}
combined_validated_tf_list <- c(rr_list, mm_list, mr_list, rm_list)
ggplot(data.frame(combined_validated_tf_list), aes(x=combined_validated_tf_list)) + geom_histogram(stat = "count", fill = "seagreen") + scale_y_continuous(breaks = seq(0,12,by=2)) + xlab(label = "TFs identified") + ggtitle("Top TF Cross-validation Frequency")

```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
 