---
title: "GO_enrichment_analysis"
author: "Ashton Omdahl"
date: "April 13, 2018"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(tidyr)
library(magrittr)
```
#Go Enrichment Analysis
First let's look at the MA modules
```{r}
setwd("D:/AshtonData/MPI_all_data/GO_enrichment_analysis")
ma_go_terms <- read_tsv("ma_go_genes_modules.tsv") %T>% print()
ma_go_terms %>% count(Module, GO_ID) %>% arrange(desc(n)) -> ma_go_term_counts
hist(ma_go_term_counts$n,breaks = seq(0,300,by=10))

```

First let's look at the RNA-seq modules
```{r}
setwd("D:/AshtonData/MPI_all_data/GO_enrichment_analysis")
RNA_go_terms <- read_tsv("rna_go_genes_modules.tsv") %T>% print()
RNA_go_terms %>% count(Module, GO_ID) %>% arrange(desc(n)) -> RNA_go_term_counts
hist(RNA_go_term_counts$n, breaks = seq(0,300,by=10))

```

So it looks like most go_terms appear pretty arbitrarily, but some very few are enriched.
##Permutation testing
We want to pick ones that are statistically significant for the population. To determine this, we need to do some classy permutation testing (!).
To do this, I constructed a script 'GO_enrichment_analysis.R.'

Now, to see if any of our enrichment calculations actually were significant in someway.

First, let's read in the sizes
```{r}
rna_module_sizes <- data.frame("Module" =c("turquoise", "blue", "brown", "yellow", "green", "red", "black", "pink", "magenta", "purple", "greenyellow", "tan", "salmon", "cyan", "midnightblue", "lightcyan", "lightgreen", "lightyellow", "royalblue", "darkred", "darkgreen", "darkturquoise", "darkgrey", "orange", "darkorange", "white", "skyblue", "saddlebrown", "paleturquoise", "steelblue", "violet", "gre60"), "Size" = c(999, 982, 908, 846, 784, 749, 667, 604, 578, 526, 473, 279, 273, 148, 131, 119, 101, 74, 73, 72, 63, 58, 54, 51, 47, 45, 40, 38, 35, 35, 34, 114))
MA_module_sizes <- data.frame("Module" = c("turquoise", "blue", "brown", "yellow", "green", "red", "black", "pink", "magenta", "purple", "greenyellow", "tan", "salmon", "cyan", "midnightblue", "lightcyan", "lightgreen", "lightyellow", "royalblue", "darkred", "darkgreen", "darkturquoise", "darkgrey", "orange", "darkorange", "white", "skyblue", "saddlebrown", "steelblue", "paleturquoise", "violet", "darkolivegreen", "darkmagenta", "grey60"), "Size" = c(946, 829, 790, 780, 677, 577, 552, 432, 379, 370, 362, 337, 328, 245, 213, 206, 173, 156, 128, 127, 119, 113, 112, 110, 106, 106, 100, 97, 77, 70, 66, 58, 53, 206))
```

So now, for a given module, we want to 
```{r}
inner_join(RNA_go_term_counts, rna_module_sizes, by = c("Module")) %>% rename("ModuleSize" = Size) -> rna_enrichment_sizes
write_tsv(rna_enrichment_sizes, "D:/AshtonData/MPI_all_data/GO_enrichment_analysis/rna_enrichment_sizes.txt")
#Read in what you want to compare it to

pValReportingRNA <- function(goid, module_name)
{
  file_name <- paste0("D:/AshtonData/MPI_all_data/GO_enrichment_analysis/RNA_permutations/rna_", module_name, ".txt")
  f_in <- read_tsv(file_name)
  f_in %>% filter(GO_ID == goid) -> sto
  unlist(as.numeric(sto[-1]),use.names = F) -> sto
  #Lookup the value
  lookup_val <- (RNA_go_term_counts %>% filter(Module == module_name, GO_ID == goid))$n
  val <- sum(sto >= lookup_val)
  val/1000
}
rna_p_vals <- rna_enrichment_sizes %>% filter(n>=50) %>% mutate("pval" = 

                                                                   
```
So I got it to run in a script I want, but let's test it some more.
Yellow has 151 genes enriched with the GO:0006412 GO term. How likely is that by random chance?
```{r}
rna_yellow <- read_tsv("D:/AshtonData/MPI_all_data/GO_enrichment_analysis/RNA_permutations/rna_yellow.txt")
rna_yellow %>% filter(GO_ID == "GO:0006412")-> yellow_t
as.numeric(yellow_t[-1]) -> yellow_t
sum(yellow_t > 151)
summary(yellow_t)
```

This means that none of the permutations had this many, so its highly unlikely that it just random chance. WHOHOOO!